---
title: "lab10"
author: "Narjes Mathlouthi"
date: "11/30/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(tidyverse)
library(janitor)
library(usethis)
library(sf)
library(jsonlite)
library(multicolor)
```

##  beepr beeps

Use the function `beep()` in the beeper package to make an audio 


```{r}

#beep()
#beep(8)

```

Vector of values that our `for` loop will iterate over
rev(seq (1:99))

```{r, eval = FALSE}
for ( i in rev(seq(1:9999))) {
  print(paste(i," bottle of beer on the wall"))
}
#beep(4)
```

## praise and cowsay
Packages built with a single purpose: to be kind and fun

```{r}
praise("${Exclamation}, ${EXCLAMATION}!!!!")

praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}!")
```

USE cowsay::say()to make a character say something to you

```{r}
say("hello world",
   by = "hypnotoad",
   what_color = c("royalblue1", "tomato2"),
 by_color = c("rainbow", "rainbow"))
```

Convert to a git `usethis` package 
```{r}
#Convert to git and github repo
#usethis::use_git()
#usethis::use_github()
```

## paletteer to access thousands of colors palettes

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  #find the 10 storm with the lowest minimum storm
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  
  geom_col(aes(fill = name)) +
#View(palettes_d_names)
  scale_fill_paletteer_d("ggsci::cyan_material")

```
## One spatial data example

```{r}
vegetation <- read_sf("doc.kml") %>% 
  select(Name) %>% 
  janitor::clean_names()


#create  a map 
ggplot(data= vegetation) +
  geom_sf(aes(fill = name), color = NA) + 
  theme_minimal() +
  scale_fill_paletteer_d("ggthemes::manyeys") +
  labs(title = "Jordana Basin LTER Vegetation", 
       caption = "Soursce : Jordana LTER")
  

#Update theme to be theme minimal
#Fill color change based on vegetation
#color of line to NA (color = NA) outside of aes because it's not a var


```

```{r}
# the default is to save the last plot
ggsave(filename = "my_awesome_map.jpg", width = 8, height = 5, bg = "black")
```

